### 2013-06-24 trunk/network-science/paper.tex

\begin{center} \begin{tikzpicture}
  \begin{axis}[ 
    xlabel={$z$},
    ylabel={evolving activity}
  ] 
  \addplot[color=blue!50!black,samples=300,domain=-20:-0.001] {exp(ln(10)*(1/x))}; 
  \addplot[color=green!50!black,samples=300,domain=-20:-0.001] {exp(ln(100)*(1/x))}; 
  \addplot[color=red!50!black,samples=300,domain=-20:-0.001] {exp(ln(1000)*(1/x))}; 
  \end{axis}
\end{tikzpicture}

\begin{color}{blue!50!black}blue
\end{color}: $\mu=10$,
\begin{color}{green!50!black}green
\end{color}: $\mu=100$,
\begin{color}{red!50!black}red
\end{color}: $\mu=1000$\end{center}

@@

\subsection{Optimization and Parallelizability}

In most cases, we only need to query the latest properties of the graph, i.e.,
$t=\mathit{currentTime}$. And we observe that in Algorithm \ref{alg-con},
\ref{alg-deg} and \ref{alg-act}, the binary search can be replace by simply find
the last entry of the argument sequence. So those three algorithms can be done
in $O(1)$ time if we do not perform historical queries.

Algorithm \ref{alg-cen} actually repeat the computation of the multiplication
of a sparse matrix to a vector, which is highly parallelizable[?]. So in a large
scale distributed system, we can perform very efficient analysis to an evolving
graph, by our model.
\section{Experiment}
\subsection{Data Generation} 
Our data generation is base on real social networks provided by \cite{database1,
database2}. Unfortunatly, those databases do not contain evolving history
recorded data, so we simulate the evolving history by use the
authentic graph as the final state of the tested dynamic graph.
We give a random permutation to the edges, in a way such that there will always
be just one component -- known as the giant component. Because the final state
is from real world data, it is ensured 
the evolving graph generated by our model will satisfy all the property that we
discussed in section 2.2. In addition, Kumar introduced another way to generate
artificial data of evolving social networks\cite{kumar2010structure}.

\subsection{Program}
We have implemented the algorithms using C++ language without compiler
optimization, and all execution is done under a typical PC with Intel Core i3
M380.

>>>>

\begin{center} \begin{tikzpicture} \begin{axis}[ 
	thick,
	xmax=5, ymax=1,
	axis line style=very thick,
	axis x line=bottom,
	axis y line=left,
	xlabel={$z$},
	ylabel={evolving activity},
        legend pos=outer north east
] 
	\addplot[color=blue!50!black,samples=300,domain=-20:-0.001] {exp(ln(10)*(1/x))}; 
	\addplot[color=green!50!black,samples=300,domain=-20:-0.001] {exp(ln(100)*(1/x))}; 
	\addplot[color=red!50!black,samples=300,domain=-20:-0.001] {exp(ln(1000)*(1/x))}; 
	\legend{$\mu=10$,$\mu=100$,$\mu=1000$};
	\end{axis} \end{tikzpicture} 
\end{center}

@@

\subsection{Optimization and Parallelization}
In most cases, we only need to query the latest properties of the graph, i.e.,
$t=\mathit{currentTime}$. And we observe that in algorithm \ref{alg-con},
\ref{alg-deg} and \ref{alg-act}, the binary search can be replace by simply find
the last entry of the argument sequence. So those three algorithms can be done
in $O(1)$ time if we do not perform historical queries.

What algorithm \ref{alg-cen} do is only the multiplication of a sparse matrix
to a vector, which is a classical problem called sparse matrix-vector
multiplication (SpMV). This problem can be easily solve in both
throughput-oriented and latency-oriented processors in
parallel\cite{williams2009optimization, bell2008efficient,
bell2009implementing, catalyurek1999hypergraph, zhuo2005sparse}.  This is a
good news to us because nowadays parallel machine is much more common in
company, research facilities and even with desktop computer, thanks to the
emergence of GPGPU platforms such as CUDA and OpenCL.

\section{Experiment}
\subsection{Data Generation} 
Our data generation is base on real social networks provided by \cite{database1,
database2}. Unfortunately, those databases do not contain evolving history
recorded data, so we simulate the evolving history by use the
authentic graph as the final state of the tested dynamic graph.
We give a random permutation to the edges, in a way such that there will always
be just one component -- known as the giant component. Because the final state
is from real world data, it is ensured 
the evolving graph generated by our model will satisfy all the property that we
discussed in section 2.2. In addition, Kumar introduced another way to generate
artificial data of evolving social networks\cite{kumar2010structure}.

\subsection{Program}
We have implemented the algorithms using C++ language without compiler
optimization, and all execution is done under a typical PC with 
Intel (R) Core (TM) i3 CPU M380  @ 2.53GHz, 2GB RAM.
